### 2014-01-22 thesis/src/chapters/chapter-state-of-the-art.tex
Thesis: summary of oneflow section

\subsection{Summary}

>>>>

\subsection{Summary}
Taking everything into consideration, OneFlow is a valuable addition to OpenNebula ecosystem. Undoubtedly, its auto-scaling feature with elastic policy mechanism cannot be underestimated. However, actions taken by scaling mechanism are coarse-grained by being limited to a horizontal scaling. What makes things worse, OneFlow can not leverage resources of multiple providers associated within a cloud federation.
